Sandbox BC Data

### 2020-11-16 scripts/draft_play.Rmd
Moved Joe's code around

```{r setup, include = FALSE, echo = FALSE, warning = FALSE}
library("papaja")
r_refs("r-references.bib")
library(here)
library(tidyverse)
library("readxl")

@@

district_class <- bc_data_district_classification %>%
  select("SCHOOL_YEAR",
         "DATA_LEVEL",
         "PUBLIC_OR_INDEPENDENT",
         "DISTRICT_NUMBER",
         "DISTRICT_NAME",
         "DISTRICT_POPULATION_2016",
         "DISTRICT_CLASSIFICATION",
         "SPECIAL_NEEDS_CODE",
         "NUMBER_OF_STUDENTS") %>%
  filter(DATA_LEVEL == "DISTRICT LEVEL",
         PUBLIC_OR_INDEPENDENT == "BC Public School")

@@

>>>>

```{r setup, include = FALSE, echo = FALSE, warning = FALSE}
library("papaja")
r_refs("r-references.bib")
library(here)
library(tidyverse)
library("readxl")
library(janitor)

@@

district_class <- bc_data_district_classification %>%
  select("SCHOOL_YEAR",
         "DATA_LEVEL",
         "PUBLIC_OR_INDEPENDENT",
         "DISTRICT_NUMBER",
         "DISTRICT_NAME",
         "DISTRICT_POPULATION_2016",
         "DISTRICT_CLASSIFICATION",
         "SPECIAL_NEEDS_CODE",
         "NUMBER_OF_STUDENTS") %>%
  filter(DATA_LEVEL == "DISTRICT LEVEL",
         PUBLIC_OR_INDEPENDENT == "BC Public School") %>%
  remove_empty_rows()

@@

```{r cleaning Oregon data}
primodata <- read_excel(here("data", "primo_merged_oregon_data.xlsx"))
cleanest_primo <-primodata %>% 
  remove_empty(which = c("rows", "cols")) %>% 
  clean_names()

cleanest_primo <- cleanest_primo %>% 
  select(-six_to_twentyone_total, -x24)

cleanest_primo2 <- cleanest_primo [!(cleanest_primo$disability=="TOTAL (SUM OF ALL OF THE ABOVE)" |cleanest_primo$disability=="OTHER HEALTH IMPAIRMENT" | cleanest_primo$disability=="SPECIFIC LEARNING DISABILITY" | cleanest_primo$disability=="SPECIFIC LEARNING DISABILITY"),]
cleanest_primo2

fresh_primo <- cleanest_primo2 %>% 
  pivot_longer(starts_with("x"), names_to = "age", values_to = "frequency") %>% 
  mutate(age = parse_number(age), 
         year = parse_number(year))

fresh_primo %>% 
  group_by(year, disability) %>% 
  summarize(total=sum(frequency, na.rm=TRUE))

```{r Oregon plot}

ggplot(fresh_primo, aes(age, frequency))+
  geom_line(aes(color=disability))+
  facet_wrap(~year)

```{r}
#hiding this for now
#fresh_primo %>% 
 # filter(disability=="AUTISM") %>%

#ggplot(aes(age, frequency))+
#  geom_line(aes(color=disability))+
 # facet_wrap(~year)

```
```{r}
#this is more in line with the BC graphing
#ggplot(fresh_primo, aes(year, frequency))+
# geom_smooth(color = "cornflowerblue") +
# theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#  facet_wrap(~disability)
